### 2018-08-01 doc/plos/text/manuscript.tex
wording on error relative to baseline

>>>>

To assess accuracy at finer geographic resolutions, we report MAE relative to
the naive and simple baselines (measured as the ratios MASE and RelMAE
respectively). When aggregating errors over multiple geographic units (e.g.
states within some region) we report the geometric mean of errors as this
yields a result that can still be interpreted as a ratio.
